FinalManuscript_DISCS_UG

### 2018-06-26 parts/02_relatedliterature.tex
Fixed definition of homomorphic cryptosystem.

A cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
\begin{equation}
    \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \oplus \mathcal{E}_k \left(p_2\right)
\end{equation}
where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, $k \in \mathcal{K}$ is the encryption key, and $\boxplus$ and $\oplus$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively \cite{fontaine_survey_2007}. Furthermore, suppose in a public-key cryptosystem, let $\mathcal{E}_k \left(p \right)$ be the encryption function using the public key $k$, and $\mathcal{D}_l \left(c \right)$ be the decryption function using the private key $l$. Then this cryptosystem is homomorphic if it satisfies
\begin{equation}
    p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \oplus \mathcal{E}_k \left(p_2\right) \right)
\end{equation}
where $p_1, p_2 \in \mathcal{P}$ are the plaintexts \cite{li_elliptic_2012}.
In other words, a homomorphic cryptosystem preserves the operations that can be typically done with the plaintext without the intermediary step of decrypting the ciphertext beforehand.

>>>>

Homomorphic cryptosystems are a special type of cryptosystem wherein operations can be securely performed on encrypted data. Suppose that for a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function using the public key $k \in \mathcal{K}$, and $\mathcal{D}_l \left(c \right)$ be the decryption function using the private key $l$. A cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
\begin{equation}
    \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \oplus \mathcal{E}_k \left(p_2\right)
\end{equation}
where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, and $\boxplus$ and $\oplus$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively \cite{fontaine_survey_2007}. Furthermore, a homomorphic cryptosystem also satisfies \cite{li_elliptic_2012}
\begin{equation}
    p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \oplus \mathcal{E}_k \left(p_2\right) \right).
\end{equation}
In other words, a homomorphic cryptosystem preserves the operations that can be typically done with the plaintext without the intermediary step of decrypting the ciphertext beforehand. An important note about the defintion of a homomorphic cryptosystem is that the operations $\boxplus$ and $\oplus$ need not be the same. A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.
